Predicting sales of newly published books

### 2015-10-19 paper.tex
comments on figures

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
\ref{tabla:results9} and \ref{tabla:results4}, using those categorical variables 
as part of a big data set makes the problem hard to solve, both in required 
time to build the forecasting models as well as in the obtained errors.
Moreover, some methods are unable to build the models in a reasonable time.
%However, as stated before, Trevenque expert sales manager, taking into account 
%his knowledge in industry experience and their perceptions, decided that 
%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

The Linear Regression model outperforms other complex methods, both in time 
(as it is a simple method to train) and in obtained errors.
However, more powerful models, that obtain better results, can be obtained in 
comparable time.

Taking into account the SVM model obtained results, this method obtains the lower 
errors. Even when used using the default parameter values it exhibit a good 
generalization performance.
However, it is much slower than the others to build the model, not only when 
using the dataset with categorical input variables, but also when using the 
datasets with numerical variables.

>>>>

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_time.eps,width=7cm}
\caption{\small{Running time in seconds, obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). Plot shows that using categorical variables as part of the dataset makes the problem hard to solve. As was expected, simpler methods are much faster to build the model than the complex ones.}}
\label{fig:time}
\end{center}
\end{figure}

\begin{figure}[!h] 
\begin{center}
  \epsfig{file=fig_rae.eps,width=7cm}
\caption{\small{Relative absolute error (RAE $\%$) obtained after applying the five methods to the reduced datasets (16, 9, 4 and X features each one). The M5P model obtains the lowest errors, whatever the dataset used.}}
\label{fig:rae}
\end{center}
\end{figure}

% - indicar que el uso de las dos variables categóricas hace más difícil de aprender el conjunto
Paying attention to the obtained results shown in tables \ref{tabla:resultsT}, 
\ref{tabla:resultsSOM}, \ref{tabla:results9} and \ref{tabla:results4}, 
as well as the figures \ref{fig:time} and \ref{fig:rae}, 
using those categorical variables as part of a big dataset makes the problem 
hard to solve, both in required time to build the forecasting models as well as 
in the obtained errors.
Moreover, some methods are unable to build the models in a reasonable time.
%However, as stated before, Trevenque expert sales manager, taking into account 
%his knowledge in industry experience and their perceptions, decided that 
%\emph{EDITORIAL} and \emph{SUBJECT} should be taken into account.

@@

The Linear Regression model outperforms some other complex methods, both in time 
(as it is a simple method to train) and in obtained errors.
However not in all cases, as more powerful models that obtain better results 
can be obtained in comparable time.

Taking into account the SVM model obtained results, this method obtains comparable 
errors to those of M5P. Even when used using the default parameter values it exhibit 
a good generalization performance.
However, it is much slower than the others to build the model, not only when 
using the dataset with categorical input variables, but also when using the 
datasets with numerical variables.
